---
title: "logistic_regression_on_socialNetworkAds_R"
output: html_document
---

# In this task , we are doing logistic regression on it basically logistic regression gets 0 or 1 value means ture or false . about the task we have the data of who is puchased ads.

## firstly, we load the data from the csv files becouase we have data in csv format and see the data


```{r setup, include=FALSE}
library(readr)

dataLoad <- read_csv("Social_Network_Ads.csv")
head(dataLoad)

```

## user id is not imp for our dataset so we remove it
##  table function is most important it helps for barplot for gender

```{r cars}
dataLoad$`User ID` = NULL
barplot(table(dataLoad$Gender))
```

# scaling of the data
# converting the purchase column in factor


```{r pressure, echo=FALSE}
dataLoad$Purchased = factor(dataLoad$Purchased, levels = c(0,1))
head(dataLoad)

dataLoad[,2:3] = scale(dataLoad[,2:3])
head(dataLoad)
```

# create train and test dataset with the help of caTools

```{r}
library(caTools)

set.seed(123)


split = sample.split(dataLoad$Purchased, SplitRatio = 0.75)
train = subset(dataLoad, split == T)
test = subset(dataLoad, split == F)

```


# creat a modal
# glm stands for generalise linear modal 

```{r}
classifier <- glm(formula = Purchased~., family = "binomial", data = train)
summary(classifier)

```

# prediction
```{r}
predict = predict(classifier, test, type = "response")
predict
```

# response means is the way of telling R to generate output in the form of probability   
```{r}
test$prediction <- predict
head(test)

```

# we can ifelse function use for if greater then 0.5 then eqaul to 1 and less then equal to 0
```{r}
test$probabilityAnswer <- ifelse(test$prediction <= 0.5,  0 , 1) 
test

table(test$Purchased, test$probabilityAnswer)
table(test$probabilityAnswer)
```

# total accuracy is 83 = 57 + 26
# and this is called confussion matrix



